What's hot and what's not:\\Windowed developer topic analysis

### 2011-09-02 src/validate/output/maxdb.mulan.out.tex
Mulan parser and new run of data

\begin{tabular}{l|rrrrrrrr}

  & BR & CLR & HOMER & IncludeLabels & LP & MLStacking & MLkNN & RAkEL \\

@@

example-Accuracy & 0.49 & 0.47 & 0.51 & 0.44 & 0.42 & 0.47 & 0.43 & 0.48 \\

example-Fmeasure & 0.55 & 0.50 & 0.53 & 0.45 & 0.44 & 0.48 & 0.43 & 0.50 \\

example-HammingLoss & 0.19 & 0.14 & 0.14 & 0.14 & 0.17 & 0.13 & 0.13 & 0.13 \\

example-Precision & 0.50 & 0.49 & 0.53 & 0.45 & 0.45 & 0.49 & 0.43 & 0.51 \\

example-Recall & 0.61 & 0.50 & 0.53 & 0.45 & 0.43 & 0.47 & 0.43 & 0.50 \\

example-SubsetAccuracy & 0.40 & 0.43 & 0.45 & 0.43 & 0.38 & 0.43 & 0.43 & 0.43 \\

label-macro-AUC & NaN & NaN & NaN & NaN & NaN & NaN & NaN & NaN \\

label-macro-F1 & 0.32 & 0.19 & 0.23 & 0.11 & 0.19 & 0.12 & 0.00 & 0.26 \\

label-macro-Precision & 0.29 & 0.31 & 0.32 & 0.21 & 0.23 & 0.18 & 0.00 & 0.40 \\

label-macro-Recall & 0.38 & 0.15 & 0.20 & 0.08 & 0.17 & 0.10 & 0.00 & 0.23 \\

label-micro-AUC & 0.76 & 0.66 & 0.62 & 0.55 & 0.62 & 0.68 & 0.65 & 0.68 \\

label-micro-F1 & 0.39 & 0.27 & 0.34 & 0.13 & 0.25 & 0.21 & 0.00 & 0.34 \\

label-micro-Precision & 0.34 & 0.42 & 0.49 & 0.33 & 0.30 & 0.49 & 0.00 & 0.49 \\

label-micro-Recall & 0.47 & 0.21 & 0.26 & 0.09 & 0.22 & 0.14 & 0.00 & 0.27 \\

rank-AvgPrecision & 0.54 & 0.57 & 0.54 & 0.40 & 0.40 & 0.60 & 0.58 & 0.51 \\

rank-Coverage & 1.40 & 1.23 & 1.43 & 1.84 & 1.93 & 1.16 & 1.20 & 1.54 \\

rank-One-error & 0.81 & 0.79 & 0.81 & 0.90 & 0.89 & 0.76 & 0.79 & 0.79 \\

rank-Ranking Loss & 0.41 & 0.35 & 0.41 & 0.58 & 0.60 & 0.32 & 0.33 & 0.46 \\

>>>>

\begin{tabular}{l|rrrrrrrrr}

  & BR & CLR & HOMER & IncludeLabels & LP & MC-Copy & MC-Ignore & MLkNN & RAkEL \\

@@

Average Precision & 0.53 & 0.59 & 0.52 & 0.56 & 0.47 & 0.52 & 0.55 & 0.58 & 0.54 \\

Coverage & 1.41 & 1.19 & 1.44 & 1.33 & 1.82 & 1.52 & 1.54 & 1.21 & 1.49 \\

ErrorSetSize & 1.42 & 1.13 & 1.38 & 1.29 & 1.87 & 1.49 & 1.54 & 1.14 & 1.43 \\

Example-Based Accuracy & NaN & NaN & NaN & NaN & NaN &  &  & NaN & NaN \\

Example-Based F Measure & NaN & NaN & NaN & NaN & NaN &  &  & NaN & NaN \\

Example-Based Precision & NaN & NaN & NaN & NaN & NaN &  &  & NaN & NaN \\

Example-Based Recall & NaN & NaN & NaN & NaN & NaN &  &  & NaN & NaN \\

Hamming Loss & 0.19 & 0.14 & 0.13 & 0.14 & 0.17 &  &  & 0.13 & 0.14 \\

IsError & 0.44 & 0.41 & 0.45 & 0.42 & 0.46 & 0.44 & 0.41 & 0.42 & 0.42 \\

Macro-averaged AUC & NaN & NaN & NaN & NaN & NaN &  &  & NaN & NaN \\

Macro-averaged F-Measure & NaN & NaN & NaN & NaN & NaN &  &  & NaN & NaN \\

Macro-averaged Precision & NaN & NaN & NaN & NaN & NaN &  &  & NaN & NaN \\

Macro-averaged Recall & NaN & NaN & NaN & NaN & NaN &  &  & NaN & NaN \\

Mean Average Precision & NaN & NaN & NaN & NaN & NaN &  &  & NaN & NaN \\

Micro-averaged AUC & 0.77 & 0.67 & 0.61 & 0.77 & 0.74 &  &  & 0.69 & 0.72 \\

Micro-averaged F-Measure & 0.39 & 0.36 & 0.37 & 0.34 & 0.33 &  &  & NaN & 0.34 \\

Micro-averaged Precision & 0.34 & 0.44 & 0.52 & 0.44 & 0.35 &  &  & NaN & 0.44 \\

Micro-averaged Recall & 0.47 & 0.31 & 0.30 & 0.29 & 0.32 &  &  & 0.00 & 0.28 \\

OneError & 0.83 & 0.78 & 0.83 & 0.79 & 0.83 & 0.81 & 0.78 & 0.79 & 0.79 \\

Ranking Loss & 0.23 & 0.19 & 0.24 & 0.22 & 0.31 &  &  & 0.19 & 0.24 \\

Subset Accuracy & 0.41 & 0.48 & 0.50 & 0.50 & 0.53 &  &  & 0.43 & 0.51 \\

### 2011-09-02 src/validate/output/maxdb.mulan.out.transpose.tex
Mulan parser and new run of data

\begin{tabular}{l|rrrrrrrrrrrrrrrrrr}

  & example-Accuracy & example-Fmeasure & example-HammingLoss & example-Precision & example-Recall & example-SubsetAccuracy & label-macro-AUC & label-macro-F1 & label-macro-Precision & label-macro-Recall & label-micro-AUC & label-micro-F1 & label-micro-Precision & label-micro-Recall & rank-AvgPrecision & rank-Coverage & rank-One-error & rank-Ranking Loss \\

@@

BR & 0.49 & 0.55 & 0.19 & 0.50 & 0.61 & 0.40 & NaN & 0.32 & 0.29 & 0.38 & 0.76 & 0.39 & 0.34 & 0.47 & 0.54 & 1.40 & 0.81 & 0.41 \\

CLR & 0.47 & 0.50 & 0.14 & 0.49 & 0.50 & 0.43 & NaN & 0.19 & 0.31 & 0.15 & 0.66 & 0.27 & 0.42 & 0.21 & 0.57 & 1.23 & 0.79 & 0.35 \\

HOMER & 0.51 & 0.53 & 0.14 & 0.53 & 0.53 & 0.45 & NaN & 0.23 & 0.32 & 0.20 & 0.62 & 0.34 & 0.49 & 0.26 & 0.54 & 1.43 & 0.81 & 0.41 \\

IncludeLabels & 0.44 & 0.45 & 0.14 & 0.45 & 0.45 & 0.43 & NaN & 0.11 & 0.21 & 0.08 & 0.55 & 0.13 & 0.33 & 0.09 & 0.40 & 1.84 & 0.90 & 0.58 \\

LP & 0.42 & 0.44 & 0.17 & 0.45 & 0.43 & 0.38 & NaN & 0.19 & 0.23 & 0.17 & 0.62 & 0.25 & 0.30 & 0.22 & 0.40 & 1.93 & 0.89 & 0.60 \\

MLStacking & 0.47 & 0.48 & 0.13 & 0.49 & 0.47 & 0.43 & NaN & 0.12 & 0.18 & 0.10 & 0.68 & 0.21 & 0.49 & 0.14 & 0.60 & 1.16 & 0.76 & 0.32 \\

MLkNN & 0.43 & 0.43 & 0.13 & 0.43 & 0.43 & 0.43 & NaN & 0.00 & 0.00 & 0.00 & 0.65 & 0.00 & 0.00 & 0.00 & 0.58 & 1.20 & 0.79 & 0.33 \\

RAkEL & 0.48 & 0.50 & 0.13 & 0.51 & 0.50 & 0.43 & NaN & 0.26 & 0.40 & 0.23 & 0.68 & 0.34 & 0.49 & 0.27 & 0.51 & 1.54 & 0.79 & 0.46 \\

>>>>

\begin{tabular}{l|rrrrrrrrrrrrrrrrrrrrr}

  & Average Precision & Coverage & ErrorSetSize & Example-Based Accuracy & Example-Based F Measure & Example-Based Precision & Example-Based Recall & Hamming Loss & IsError & Macro-averaged AUC & Macro-averaged F-Measure & Macro-averaged Precision & Macro-averaged Recall & Mean Average Precision & Micro-averaged AUC & Micro-averaged F-Measure & Micro-averaged Precision & Micro-averaged Recall & OneError & Ranking Loss & Subset Accuracy \\

@@

BR & 0.53 & 1.41 & 1.42 & NaN & NaN & NaN & NaN & 0.19 & 0.44 & NaN & NaN & NaN & NaN & NaN & 0.77 & 0.39 & 0.34 & 0.47 & 0.83 & 0.23 & 0.41 \\

CLR & 0.59 & 1.19 & 1.13 & NaN & NaN & NaN & NaN & 0.14 & 0.41 & NaN & NaN & NaN & NaN & NaN & 0.67 & 0.36 & 0.44 & 0.31 & 0.78 & 0.19 & 0.48 \\

HOMER & 0.52 & 1.44 & 1.38 & NaN & NaN & NaN & NaN & 0.13 & 0.45 & NaN & NaN & NaN & NaN & NaN & 0.61 & 0.37 & 0.52 & 0.30 & 0.83 & 0.24 & 0.50 \\

IncludeLabels & 0.56 & 1.33 & 1.29 & NaN & NaN & NaN & NaN & 0.14 & 0.42 & NaN & NaN & NaN & NaN & NaN & 0.77 & 0.34 & 0.44 & 0.29 & 0.79 & 0.22 & 0.50 \\

LP & 0.47 & 1.82 & 1.87 & NaN & NaN & NaN & NaN & 0.17 & 0.46 & NaN & NaN & NaN & NaN & NaN & 0.74 & 0.33 & 0.35 & 0.32 & 0.83 & 0.31 & 0.53 \\

MC-Copy & 0.52 & 1.52 & 1.49 &  &  &  &  &  & 0.44 &  &  &  &  &  &  &  &  &  & 0.81 &  &  \\

MC-Ignore & 0.55 & 1.54 & 1.54 &  &  &  &  &  & 0.41 &  &  &  &  &  &  &  &  &  & 0.78 &  &  \\

MLkNN & 0.58 & 1.21 & 1.14 & NaN & NaN & NaN & NaN & 0.13 & 0.42 & NaN & NaN & NaN & NaN & NaN & 0.69 & NaN & NaN & 0.00 & 0.79 & 0.19 & 0.43 \\

RAkEL & 0.54 & 1.49 & 1.43 & NaN & NaN & NaN & NaN & 0.14 & 0.42 & NaN & NaN & NaN & NaN & NaN & 0.72 & 0.34 & 0.44 & 0.28 & 0.79 & 0.24 & 0.51 \\

### 2011-09-02 src/validate/output/mysql.mulan.out.tex
Updating to a newer version of mulan
Mulan parser and new run of data

example-Accuracy & 0.45 & 0.40 & 0.50 & 0.40 & 0.40 & 0.38 & 0.33 & 0.48 \\

example-Fmeasure & 0.56 & 0.48 & 0.59 & 0.47 & 0.49 & 0.46 & 0.40 & 0.55 \\

example-HammingLoss & 0.24 & 0.19 & 0.18 & 0.19 & 0.23 & 0.19 & 0.20 & 0.17 \\

example-Precision & 0.50 & 0.51 & 0.60 & 0.52 & 0.52 & 0.50 & 0.44 & 0.60 \\

example-Recall & 0.65 & 0.46 & 0.58 & 0.44 & 0.47 & 0.43 & 0.37 & 0.52 \\

example-SubsetAccuracy & 0.19 & 0.24 & 0.31 & 0.24 & 0.23 & 0.23 & 0.20 & 0.31 \\

label-macro-AUC & 0.74 & 0.66 & 0.64 & 0.60 & 0.56 & 0.58 & 0.59 & 0.67 \\

label-macro-F1 & 0.46 & 0.30 & 0.43 & 0.28 & 0.32 & 0.27 & 0.22 & 0.39 \\

label-macro-Precision & 0.41 & 0.41 & 0.49 & 0.39 & 0.37 & 0.34 & 0.34 & 0.52 \\

label-macro-Recall & 0.56 & 0.26 & 0.40 & 0.24 & 0.31 & 0.23 & 0.19 & 0.33 \\

label-micro-AUC & 0.81 & 0.81 & 0.77 & 0.77 & 0.66 & 0.80 & 0.80 & 0.79 \\

label-micro-F1 & 0.59 & 0.53 & 0.61 & 0.51 & 0.50 & 0.51 & 0.45 & 0.59 \\

label-micro-Precision & 0.51 & 0.69 & 0.66 & 0.71 & 0.53 & 0.70 & 0.69 & 0.73 \\

label-micro-Recall & 0.68 & 0.43 & 0.56 & 0.41 & 0.48 & 0.41 & 0.34 & 0.49 \\

rank-AvgPrecision & 0.76 & 0.77 & 0.69 & 0.72 & 0.53 & 0.74 & 0.76 & 0.73 \\

rank-Coverage & 1.51 & 1.47 & 1.94 & 1.72 & 2.99 & 1.57 & 1.54 & 2.00 \\

rank-One-error & 0.40 & 0.39 & 0.47 & 0.44 & 0.63 & 0.43 & 0.40 & 0.36 \\

rank-Ranking Loss & 0.19 & 0.18 & 0.27 & 0.22 & 0.52 & 0.20 & 0.19 & 0.28 \\

>>>>

Average Precision & 0.76 & 0.76 & 0.69 & 0.73 & 0.53 & 0.72 & 0.68 & 0.75 & 0.74 \\

Coverage & 1.67 & 1.64 & 2.24 & 1.87 & 3.14 & 1.88 & 2.35 & 1.69 & 2.01 \\

ErrorSetSize & 1.23 & 1.18 & 1.90 & 1.48 & 3.49 & 1.49 & 2.10 & 1.25 & 1.59 \\

Example-Based Accuracy & NaN & NaN & NaN & NaN & NaN &  &  & NaN & NaN \\

Example-Based F Measure & NaN & NaN & NaN & NaN & NaN &  &  & NaN & NaN \\

Example-Based Precision & NaN & NaN & NaN & NaN & NaN &  &  & NaN & NaN \\

Example-Based Recall & NaN & NaN & NaN & NaN & NaN &  &  & NaN & NaN \\

Hamming Loss & 0.25 & 0.21 & 0.20 & 0.21 & 0.25 &  &  & 0.22 & 0.20 \\

IsError & 0.55 & 0.52 & 0.62 & 0.57 & 0.74 & 0.57 & 0.64 & 0.54 & 0.55 \\

Macro-averaged AUC & 0.74 & 0.65 & 0.64 & 0.61 & 0.59 &  &  & 0.62 & 0.68 \\

Macro-averaged F-Measure & NaN & NaN & NaN & NaN & NaN &  &  & NaN & NaN \\

Macro-averaged Precision & 0.42 & NaN & NaN & NaN & NaN &  &  & NaN & NaN \\

Macro-averaged Recall & 0.57 & 0.30 & 0.45 & 0.27 & 0.33 &  &  & 0.22 & 0.34 \\

Mean Average Precision & 0.53 & 0.44 & 0.45 & 0.42 & 0.39 &  &  & 0.41 & 0.50 \\

Micro-averaged AUC & 0.81 & 0.80 & 0.74 & 0.77 & 0.66 &  &  & 0.79 & 0.80 \\

Micro-averaged F-Measure & 0.59 & 0.54 & 0.61 & 0.52 & 0.50 &  &  & 0.48 & 0.56 \\

Micro-averaged Precision & 0.52 & 0.65 & 0.63 & 0.67 & 0.53 &  &  & 0.67 & 0.66 \\

Micro-averaged Recall & 0.69 & 0.47 & 0.59 & 0.43 & 0.46 &  &  & 0.38 & 0.49 \\

OneError & 0.39 & 0.38 & 0.45 & 0.41 & 0.62 & 0.42 & 0.44 & 0.39 & 0.37 \\

Ranking Loss & 0.18 & 0.18 & 0.28 & 0.22 & 0.50 &  &  & 0.19 & 0.24 \\

Subset Accuracy & 0.18 & 0.22 & 0.30 & 0.23 & 0.25 &  &  & 0.22 & 0.29 \\

### 2011-09-02 src/validate/output/mysql.mulan.out.transpose.tex
Mulan parser and new run of data

BR & 0.45 & 0.56 & 0.24 & 0.50 & 0.65 & 0.19 & 0.74 & 0.46 & 0.41 & 0.56 & 0.81 & 0.59 & 0.51 & 0.68 & 0.76 & 1.51 & 0.40 & 0.19 \\

CLR & 0.40 & 0.48 & 0.19 & 0.51 & 0.46 & 0.24 & 0.66 & 0.30 & 0.41 & 0.26 & 0.81 & 0.53 & 0.69 & 0.43 & 0.77 & 1.47 & 0.39 & 0.18 \\

HOMER & 0.50 & 0.59 & 0.18 & 0.60 & 0.58 & 0.31 & 0.64 & 0.43 & 0.49 & 0.40 & 0.77 & 0.61 & 0.66 & 0.56 & 0.69 & 1.94 & 0.47 & 0.27 \\

IncludeLabels & 0.40 & 0.47 & 0.19 & 0.52 & 0.44 & 0.24 & 0.60 & 0.28 & 0.39 & 0.24 & 0.77 & 0.51 & 0.71 & 0.41 & 0.72 & 1.72 & 0.44 & 0.22 \\

LP & 0.40 & 0.49 & 0.23 & 0.52 & 0.47 & 0.23 & 0.56 & 0.32 & 0.37 & 0.31 & 0.66 & 0.50 & 0.53 & 0.48 & 0.53 & 2.99 & 0.63 & 0.52 \\

MLStacking & 0.38 & 0.46 & 0.19 & 0.50 & 0.43 & 0.23 & 0.58 & 0.27 & 0.34 & 0.23 & 0.80 & 0.51 & 0.70 & 0.41 & 0.74 & 1.57 & 0.43 & 0.20 \\

MLkNN & 0.33 & 0.40 & 0.20 & 0.44 & 0.37 & 0.20 & 0.59 & 0.22 & 0.34 & 0.19 & 0.80 & 0.45 & 0.69 & 0.34 & 0.76 & 1.54 & 0.40 & 0.19 \\

RAkEL & 0.48 & 0.55 & 0.17 & 0.60 & 0.52 & 0.31 & 0.67 & 0.39 & 0.52 & 0.33 & 0.79 & 0.59 & 0.73 & 0.49 & 0.73 & 2.00 & 0.36 & 0.28 \\

>>>>

BR & 0.76 & 1.67 & 1.23 & NaN & NaN & NaN & NaN & 0.25 & 0.55 & 0.74 & NaN & 0.42 & 0.57 & 0.53 & 0.81 & 0.59 & 0.52 & 0.69 & 0.39 & 0.18 & 0.18 \\

CLR & 0.76 & 1.64 & 1.18 & NaN & NaN & NaN & NaN & 0.21 & 0.52 & 0.65 & NaN & NaN & 0.30 & 0.44 & 0.80 & 0.54 & 0.65 & 0.47 & 0.38 & 0.18 & 0.22 \\

HOMER & 0.69 & 2.24 & 1.90 & NaN & NaN & NaN & NaN & 0.20 & 0.62 & 0.64 & NaN & NaN & 0.45 & 0.45 & 0.74 & 0.61 & 0.63 & 0.59 & 0.45 & 0.28 & 0.30 \\

IncludeLabels & 0.73 & 1.87 & 1.48 & NaN & NaN & NaN & NaN & 0.21 & 0.57 & 0.61 & NaN & NaN & 0.27 & 0.42 & 0.77 & 0.52 & 0.67 & 0.43 & 0.41 & 0.22 & 0.23 \\

LP & 0.53 & 3.14 & 3.49 & NaN & NaN & NaN & NaN & 0.25 & 0.74 & 0.59 & NaN & NaN & 0.33 & 0.39 & 0.66 & 0.50 & 0.53 & 0.46 & 0.62 & 0.50 & 0.25 \\

MC-Copy & 0.72 & 1.88 & 1.49 &  &  &  &  &  & 0.57 &  &  &  &  &  &  &  &  &  & 0.42 &  &  \\

MC-Ignore & 0.68 & 2.35 & 2.10 &  &  &  &  &  & 0.64 &  &  &  &  &  &  &  &  &  & 0.44 &  &  \\

MLkNN & 0.75 & 1.69 & 1.25 & NaN & NaN & NaN & NaN & 0.22 & 0.54 & 0.62 & NaN & NaN & 0.22 & 0.41 & 0.79 & 0.48 & 0.67 & 0.38 & 0.39 & 0.19 & 0.22 \\

RAkEL & 0.74 & 2.01 & 1.59 & NaN & NaN & NaN & NaN & 0.20 & 0.55 & 0.68 & NaN & NaN & 0.34 & 0.50 & 0.80 & 0.56 & 0.66 & 0.49 & 0.37 & 0.24 & 0.29 \\
